\documentclass[10pt,a4paper,ragged2e,normalphoto]{template}

% Change the page layout if you need to
\geometry{left=0cm,right=0cm,marginparwidth=0cm,marginparsep=1.2cm,top=2cm,bottom=2cm}
% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[sfdefault]{arimo}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{1b1d20}
\definecolor{SlateGrey}{HTML}{444445}
\definecolor{LightGrey}{HTML}{333333}
\definecolor{DarkGrey}{HTML}{3a3d4a}
\definecolor{White}{HTML}{ffffff}
\definecolor{PaleGrey}{HTML}{333c4d}
\definecolor{SlateBlue}{HTML}{3c2eb1}


\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\colorlet{highlighter}{DarkGrey}
\colorlet{headingwhite}{White}
\colorlet{line}{PaleGrey}
\colorlet{link}{SlateBlue}

\begin{document}

\name{Shashank Simha M R}
\tagline{Tech-Enthusiast}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%   \photo{4cm}{profile.jpeg}
\personalinfo{%
  % You can add your own with \printinfo{symbol}{detail}
   \email{shashank.simha@ieee.org}
   \phone{+91 9482038408}
%  \mailaddress{Address, Street, 00000 County}
%  \location{Ulsan, South Korea}
   \github{github.com/shashank-simha}
    \homepage{simha.me}
%  \twitter{@marissamayer}
   \linkedin{linkedin.com/in/shashank-simha}
}

\newgeometry{left=0cm,right=0cm,marginparwidth=0cm,marginparsep=1.2cm,top=0cm,bottom=2cm}
\afterpage{\aftergroup\restoregeometry}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

% \begin{changemargin}{1.25cm}{1.25cm}

\summary{A tech-enthusiast currently pursuing Bachelors in Electronics and Communication Engineering. Interested in the field of Internet of Things and embedded systems. Also have good knowledge in developing websites and android applications.
\\\medskip Actively looking for opportunities for Research and Internships in the field of Embedded Systems, Internet of Things and Robotics.}

%experience section
\cvsection{Experience}

\cvevent{Jun 2019 -- Aug 2019}{Summer Research Intern}{Indian Institute of Science (IISc)}{{Worked on Implementation of Trilateration algorithm (based on RSSI) on TI-RSLK.}{Developed a self localizing robot using Robot System Learning Kit and Zigbee module.}{Successfully demonstrated the project in TI-RSLK(Max) Launch event.}{}{}}

\cvevent{May 2019 -- present}{Hub Incharge - Mysore}{IEEE Bangalore Section SAC}{{Working as Webmaster for SYWL Congress 2019.}{Coordinating Website Task force of IEEE Bangalore Section.}{}{}{}}

\cvevent{Apr 2018 -- present}{Student Coordinator}{IEEE India Council}{{Been a part of Webinars and Online Training team.}{Leading team of 5 members, for developing the official website for AISYWC'19.}{}{}{}}

\cvevent{Jun 2018 -- May 2019}{Vice-Chairperson}{NIE IEEE Student Branch}{{Led a team of 13 members, organizing over 70 events and 4 technical fests.}{Developed 2 Android apps and a Website for Events and Fests.}{Worked as the Website lead for AISYWC'18}{}{}}
%end experience section

%education section
\cvsection{Education}

\cvevent{Aug 2016 -- present}{The National Institute of Engineering}{Bachelor Degree}{{Major: Electronics and Communication}{CGPA: 9.05 (6 semesters)}{}{}{}}

\cvevent{Jul 2014 -- Apr 2016}{Maharaja's P.U. College}{11th and 12th}{{12th Score: 92.50\%}{}{}{}{}}

\cvevent{Jun 2011 -- Apr 2014}{J S S High School}{Matriculation}{{10th Score: 92.80\%}{}{}{}{}}
%end education section

%skill section
\cvsection{Skills \& Abilities}

\customskills{Embedded Systems}{{Microcontrollers and Microprocessors: 8051, x86, Atmega, Arduino,
ESP 8266, ESP 32, Raspberry Pi, MSP430, MSP432 etc.}{4}}
{{Programming Languages and Tools: Assembly, Embedded C, MATLAB, Arduino, MicroPython, Keil uVision, CCS}{4}}
{{Kernel Programming, Shell Scripting Robot Operating System(ROS) and Real Time Operating
Systems(RTOS)}{2}}
{{Communication Protocols}{4}}
{{Sensors, Actuators and Peripheral hardware}{4}}
{{Electronic Circuit Board (or PCB) design and troubleshooting}{2}}
{}{}

\customskills{Computer Programming}{{Programming Languages: C, C++, Python, PHP}{4}}
{{Full Stack Web Development}{4}}
{{Databases: MySQL, MongoDB, PostgreSQL, Firebase}{3}}
{{Frame works: Laravel, Flask, Bootstrap}{3}}
{{Android Development}{3}}
{{Computer Networks (IP Networking)}{3}}
{}{}
%end skill section

%project section
\cvsection{Projects}

\project{Dec 2017}{QM solver}{A command line application(written in python) to find minimal expressions for digital circuits by implementing Quine Mcclusky Algorithm.}{https://github.com/shashank-simha/QuineMccluskey}

\project{May 2018 -- June 2018}{NIE Summer of Code (Projects on ESP 32)}{Projects like Web server, Bluetooth SD card reader, Remote Temperature logger, OTA, Web Client, etc. built using ESP 32 and SD card module.}{https://github.com/shashank-simha/NSoC5.0}

\project{Dec 2018 -- Feb 2018}{FreeRTOS Projects}{Implementation of various features of FreeRTOS on ESP32 microcontroller.}{https://github.com/shashank-simha/FreeRTOS-Projects}

\project{Aug 2018}{Presenter}{Android app for remotely controlling presentations built using RevealJS (Integrated with Google Firebase).}{https://github.com/shashank-simha/Presenter}

\project{Jun 2018 - Oct 2018}{AISYWC Website}{Official website of All India Student-YP-WIE Congress 2018.}{https://github.com/shashank-simha/AISYWC}

\project{}{Other Projects}{All my public projects can be found at:}{https://github.com/shashank-simha/}
%end project section

%achievement section
\cvsection{Achievements}

\customitems{Technical}{Best Website Award - AISYWC'18}{}{}{}{}{}{}{}

\customitems{Others}{Secured state wise 2nd rank in National Means cum Merit Scholarship Exam (2011)}{}{}{}{}{}{}{}
%end achievement section

%interest section
\cvsection{Interests}

\customitems{Extra-curricular}{Cadet - National Cadet Corps (NCC)}{State level Swimmer}{}{}{}{}{}{}

\customitems{Hobbies}{Reading Novels}{Developing DIY projects}{}{}{}{}{}{}
%end interest section

% \end{changemargin}

\end{document}
